Women

### 2023-04-11 Code/Women.Rmd
added extra boxplot

```{r}
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = women_nations, paired = TRUE, alternative = "greater", method = "ds")
clusWilcox.test(Time, group=Year, cluster = Athlete, data = women_nations, paired = TRUE, alternative = "greater", method = "rgl")
```

>>>>

```{r}
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = women_nations, alternative = "greater", method = "ds")
#clusWilcox.test(Time, group=Year, cluster = Athlete, data = women_nations, alternative = "greater", method = "rgl")
#clusWilcox.test(Time ~ Year + cluster(Athlete), data = women_nations, alternative = "greater", method = "ds")
```
